\section{Muth--Lucas--Pischke and \cite{reis:inattentive}} \label{sec:Comparisons}

Now that our calibrations and results have been presented, we are in position to make some quantitative comparisons of our model to two principal alternatives to habit formation (or our model) for explaining excess smoothness in consumption growth, by Pischke and by Reis.

\subsection{Muth--Lucas--Pischke}
The longest-standing rival to habit formation as an explanation of consumption sluggishness is what we will call the Muth--Lucas--Pischke (henceforth, MLP) framework.  The idea is not that agents are inattentive, but instead that they have imperfect information on which they perform an optimal signal extraction problem.

\cite{muthOptimal}'s agents could observe only the level of their income, but not the split between its permanent and transitory components.  He derived the optimal (mean-squared-error-minimizing) method for estimating the level of permanent income from the observed signal about the level of actual income.  \cite{lucas:imperfectInfo} applied the same mathematical toolkit to solve a model in which firms are assumed to be unable to distinguish idiosyncratic from aggregate shocks.  \cite{pischkeMicroMacro} combines the ideas of Muth and Lucas and applies the result to micro consumption data: His consumers have no ability at all to perceive whether income shocks that hit them are aggregate or idiosyncratic, transitory or permanent.  They see only their income, and perform signal extraction on it.

Pischke calibrates his model with micro data in which he calculates that transitory shocks vastly outweigh permanent shocks.\footnote{Pischke's estimates constructed from the {\it Survey of Income and Program Participation} are rather different from the magnitudes of transitory and permanent shocks estimated in the extensive literature---mostly subsequent to Pischke's paper---cited in our calibration section above.}  So, when a shock arrives, consumers always interpret it as being almost entirely transitory and change their consumption by little.  However, macroeconometricians have long known that {\it aggregate} income shocks are close to permanent.  When an aggregate permanent shock comes along, Pischkian consumers spend very little of it, confounding the aggregate permanent shock's effect on their income with the mainly transitory idiosyncratic shocks that account for most of the total variation in their income.  This misperception causes sluggishness in {\it aggregate} consumption dynamics in response to aggregate shocks.

In its assumption that consumers fail to perceive aggregate shocks immediately and fully, Pischke's model resembles ours.  However, few papers in the subsequent literature have followed Pischke in making the assumption that households have no idea, when an idiosyncratic income shock occurs, whether it is transitory or permanent.  Especially in the last decade or so, the literature instead has almost always assumed that consumers can perfectly perceive the transitory and permanent components of their income; \hyperlink{Why-Consumers-See-Individual-Shocks}{see our defense of this assumption above}.%\footnote{The presumption that permanent idiosyncratic shocks are easily observed is bolstered by the work of \cite{lmpPermShocks}, who find that most `permanent' changes to individual income income are concentrated in periods when people change jobs or become unemployed or reemployed.  It is not plausible to assume that consumers are not aware that their income has permanently changed when they take a new job or are fired from an existing one.  Furthermore, there are at least some shocks whose transitory nature is impossible to misperceive; the best example is lottery winnings in Norway, see again \cite{fhnMPC}.  The consumption responses to those shocks resemble the responses measured in the previous literature to shocks that economists presumed (contra Pischke) that consumers knew to be transitory.  If consumers respond to such shocks in ways similar to their responses to unambiguously transitory shocks like lottery winnings, it seems hard to accept Pischke's crucial assumption that consumers treat all income shocks identically because they cannot perceive whether any given shock is transitory or permanent. A further motivation for our choice to assume that consumers perceive their idiosyncratic shocks is that our strategy has been to deviate as little as possible from the well-understood benchmark models in the micro consumption literature, which has become sufficiently widely used that they are the natural base upon which to build.  A final piece of evidence comes from some newly collected data from the Federal Reserve Bank of New York's {\it Survey of Consumer Expectations. % This has been condensed and moved to the discussion requested by a referee of our behavioral assumptions}\cite{kmpIncomeExpectations} report on results from an experiment in which consumers were asked to forecast their future income.  The actual realizations of the same consumer's income were collected in a subsequent wave of the survey.  The principal result is that consumers' mean forecast error was very close to zero.  The authors of the post (entitled ``Understanding Permanent and Temporary Income Shocks'') present the results as a confirmation of modern models' standard assumption that consumers have accurate perceptions of the dynamics of their income.}

Granting our choice to assume that consumers correctly perceive the events that are idiosyncratic to them (job changes, lottery winnings, etc), there is still a potential role for application of the MLP framework:  Instead of assuming sticky expectations, we could instead have assumed that consumers perform a signal extraction exercise on \textit{only} the aggregate component of their income, because they cannot perceive the transitory/permanent split for the (tiny) part of their income change that reflects aggregate macroeconomic developments.

In principle, such confusion could generate excess smoothness; for a detailed description of the mechanism, \hyperlink{MuthLucasPischke}{see} online Appendix~\ref{appendix:Muth}.  But, defining the signal-to-noise ratio $\varphi=\sigma^2_{\Psi}/\sigma^2_{\Theta}$, Muth's derivations imply that the optimal updating coefficient is:%\footnote{As always in a Muth-type model, the consumer is assumed to know $\sigma^2_{\Psi}$ and $\sigma^2_{\Theta}$.}
 \input{\eq/muthOptimal.tex}
\providecommand{\PischkePi}{0.83}
\providecommand{\PischkePiCancel}{0.17}
 \providecommand{\fromFile}{false}
 \providecommand{\FileOrNot}{\ifthenelse{\boolean{\fromFile}}}
Plugging our calibrations of $\sigma^2_{\Psi}$ and $\sigma^2_{\Theta}$ from section \ref{sec:calibration} into \eqref{eq:muthOptimal}, the model yields a predicted value of \FileOrNot{$1-\Pi \approx \PischkePiCancel$}{$(1-\Pi) \approx \PischkePiCancel $}---very far below the approximately $0.6$ estimate from \cite{hrsHabit} and even farther below our estimate of roughly $0.7$--$0.8$ for U.S.\ data.  This reflects the well-known fact that aggregate income is hard to distinguish from a random walk; if it were perceived to be a perfect random walk with no transitory component at all, the serial correlation in its growth would be zero.  So, in practice, allowing signal extraction with respect to the aggregate data is not a path to explaining excess smoothness.%\footnote{A further problem with the MLP approach is that it seems implausible to assume that the typical consumer would do a sophisticated Muthian signal extraction problem (really, a special case of the Kalman filter) on a single observed aggregate variable (aggregate income), when they could do much better either by adding a few more variables that are equally easy to observe (interest rates, past consumption growth, etc). If they were really so intently focused on understanding where the aggregate economy is, they could do better yet, and much more easily, just by reading the available news stories reporting on professional forecasters' forecasts.  Discomfort with this somewhat schizophrenic set of assumptions is why in work after \cite{lucas:imperfectInfo}, Lucas moved away from his assumption that microeconomic agents have imperfect information about aggregate data.}

\subsection{\cite{reis:inattentive}}

Leaving aside our earlier criticisms of its fidelity to microeconomic evidence, the model of \cite{reis:inattentive} has a further disadvantage relative to any of the other three stories (habits, MLP, or our model) with respect to aggregate dynamics. In Reis's model consumers update their information on a regular schedule---under a plausible calibration of the model, once a year. One implication of the model is that the change in consumption at the next reset is unpredictable; this implies that aggregate consumption growth would be unpredictable at any horizon beyond, say, a year.\footnote{In contrast, our model exhibits significant predictability beyond one year. The value of $\chi$ in the `horse-race' regression for the SOE economy is 0.66 when the right hand side is lagged by one quarter (see Table~\ref{tPESOEsim}). Adding an extra one and two years' lag to the right hand side sees $\chi$ decline approximately as an AR(1), to 0.20 and 0.06 respectively.}  But, business cycle analysts felt compelled to incorporate sluggishness into macroeconomic models in large part to explain the fact that consumption growth is forecastable over extended periods---empirical impulse response functions indicate that a macroeconomically substantial component of the adjustment to shocks takes place well beyond the one year horizon.  A calibration of the Reis model in which consumers update once a year therefore fails to solve a large part of the original problem (of medium-term predictability).%\footnote{A final critique of the Reis model is that, while its simplifying assumptions yield elegant and intuitive results, it is too stylized to be of much practical use in answering many questions beyond its narrow focus on matching aggregate smoothness.  A fiscal policymaker who wants to understand how various alternative policies might play out over the course of the business cycle would have a difficult time extracting plausible answers to questions like ``how much difference would it make to consumption if our fiscal stimulus took the form of extended unemployment benefits versus a temporary income tax cut.''  Our model's much greater fidelity to the microeconomic data means it might be able to provide at least somewhat plausible answers to these kinds of questions.  (Our model is an example of the broader movement in macroeconomics in recent years away from the construction stylized analytical models like Reis's to the construction of models that attempt to be taken seriously for a reasonable range of quantitative as well as qualitative predictions.)} % We've said this elsewhere

